---
title: "YouTube Video Scam Project Data Analysis"
author: "Elijah Bouma-Sims"
date: "2024-07-04"
output:
  pdf_document: default
  html_document: default
---

# Introduction

This R Markdown file contains the analysis code for the paper "The Kids Are All Right: Investigating the Susceptibility of Teens and Adults to YouTube Giveaway Scams" by Elijah Bouma-Sims, Lily Klucinec, Mandy Lanyon, Lorrie Faith Cranor, Julie Downs. paper. Please see README.md for a  descirption of all the files in this artifact.

## Requirements
Running this notebook requires the packages "dplyr", "RVAideMemoire", "rstatix", "readxl", "rcompanion", "DescTools", and "stringr".

## Code overview
In this section, we describe the structure of the code in "chronological" order. 

The code begins with a setup section that loads packages/data, creates factors, etc. Data is pulled from the ```data\df_analysis.xlsx``` In the setup code, we also create a function called ```stat_test```. This function will be used repeatedly throughout the code, so it's worth reviewing in detail. It is called to run statistical tests to check whether an outcome variable (specified by the label in ```dep_var```) varies with respect to any of our potential explanatory variables (described in Table 1 of the paper). It runs the appropriate test and computes the appropriate effect size measure based on the type of the variables. Please see the function specification for a full ist of parameters.

After the setup code, we proceed to generate tables of describe statistics for demographic variables for both adult and teen participants. The output from these code blocks was used to generate table 2 from the paper.

The next section of the document contains all of the statistical testing code. Sub-sections are named based on the dependent variable being analyzed in a particular code block, with further subdivisions as appropriate. For example, the "Legit actions" subsection contains statistical testing results for users recommended actions in response to legit stimuli. The analysis for users reactions to the YouTube video and web video are under the subheadings "Legit video" and "Legit web" respectively. 

In each statistical testing subsection, we run the ```stat_test``` function or the ```cochran.qtest``` function (for search result seleciton) to perform the statistical testing between the independent variables and the relevant dependent variable(s). If any results are significant, we use the "table" function to view how the dependent variable varies with the independent variable. Post-hoc tests run on a particular variable are listed under the appropriate heading for their dependent variable, and explicitly labeled as post-hoc results.

## Finding key statistical testing results

The length of this file is necessary to document all of the statistical tests we performed, but it can make it difficult to find particular results. To ease navigation, statistical testing results that are highlighted in the paper will begin with the text **Paper Result**. This should allow you to search the document for everywhere the term "Paper Result" appears in order to jump to those sections explicitly discussed in the paper.

# Aanlysis code
## Setup
The following code imprts packages and loads the survey data (```df_merged```). 
```{r}
library("dplyr")
library("RVAideMemoire") # for cocran q
library("rstatix") # for cramer's v
library("readxl") # to load data
library("rcompanion") # for freeman theta
library("DescTools") # for CochranArmitageTest 
library("stringr") # for str_split
data_path <- "data\\df_analysis.xlsx" # windows path
# load analysis data.
df_merged <- read_xlsx(data_path)
```

The following code creates new columns which are based upon the same question asked for Spotify and Roblox participants. For example, ```risk_usedSpotify``` and ```risk_playedRoblox```, which are the results of a question asking how frequently the participant uses spotify/plays Roblox, are merged into a new column ``risk_usedService```` 
```{r}
# usedSpotify and playedRoblox
df_merged <- df_merged %>% mutate(risk_usedService = ifelse(is.na(risk_usedSpotify), ifelse(is.na(risk_playedRoblox),NA,risk_playedRoblox), risk_usedSpotify))

# freeSpotify and freeRobux
df_merged <- df_merged %>% mutate(risk_freePremium = ifelse(is.na(risk_freeSpotify), ifelse(is.na(risk_freeRobux),NA,risk_freeRobux), risk_freeSpotify))

# spotifyPremium and purchasedRobux
df_merged <- df_merged %>% mutate(risk_purchased = ifelse(is.na(risk_spotifyPremium), ifelse(is.na(risk_puchasedRobux),NA,risk_puchasedRobux), risk_spotifyPremium))

# spotify_s and roblox_s
df_merged <- df_merged %>% mutate(risk_searchedBefore = ifelse(is.na(spotify_s), ifelse(is.na(roblox_s),NA,roblox_s), spotify_s))
```

The following code turns the columns of categorical variables into factors for proper statistical analysis.
```{r}
weekly_time_levels = c("None",  "Less than an hour", "1 to 5 hours", "5 to 10 hours", "10 to 15 hours", "15 to 20 hours", "More than 20 hours")
usage_levels = c("Never", "Once or twice", "Three to five times", "More than five times")
income_levels = c("Less than $20,000", "$20,000 to $39,999", "$40,000 to $59,999", "$60,000 to $79,999", "$80,000 to $99,999", "$100,000 to $149,999", "Over $150,000")
rank_scam_levels = c("Definitely legitimate", "Probably legitimate", "I'm not sure", "Probably a scam", "Definitely a scam")

# time factors
df_merged$time_overall <- factor(df_merged$time_overall, ordered = TRUE,levels=c("Less than 2 hours", "2 to 4 hours", "4 to 8 hours", "More than 8 hours"))
df_merged$time_computer <- factor(df_merged$time_computer, ordered = TRUE,levels=weekly_time_levels)
df_merged$time_videos <- factor(df_merged$time_videos, ordered = TRUE,levels=weekly_time_levels)
df_merged$time_mobile <- factor(df_merged$time_mobile, ordered = TRUE,levels=weekly_time_levels)
df_merged$time_nonsocial <- factor(df_merged$time_nonsocial, ordered = TRUE,levels=weekly_time_levels)
df_merged$time_social <- factor(df_merged$time_social, ordered = TRUE,levels=weekly_time_levels)

# Potential experential risk factors
df_merged$risk_coupons <- factor(df_merged$risk_coupons, ordered = TRUE,levels=usage_levels)

df_merged$risk_crypto <- factor(df_merged$risk_crypto, ordered = TRUE,levels=usage_levels)

df_merged$risk_investments <- factor(df_merged$risk_investments, ordered = TRUE,levels=usage_levels)

df_merged$risk_noRefund <- factor(df_merged$risk_noRefund, ordered = TRUE,levels=usage_levels)

df_merged$risk_onlineTasks <- factor(df_merged$risk_onlineTasks, ordered = TRUE,levels=usage_levels)

df_merged$risk_rebate <- factor(df_merged$risk_rebate, ordered = TRUE,levels=usage_levels)

df_merged$risk_usedSpotify <- factor(df_merged$risk_usedSpotify, ordered = TRUE,levels=usage_levels)

df_merged$risk_playedRoblox <- factor(df_merged$risk_playedRoblox, ordered = TRUE,levels=usage_levels)

df_merged$often_onlinetask <- factor(df_merged$often_onlinetask, ordered = TRUE, levels=usage_levels)

df_merged$risk_usedService <- factor(df_merged$risk_usedService, ordered = TRUE,levels=usage_levels)

# Ranking
df_merged$rank_legit <- factor(df_merged$rank_legit, levels=rank_scam_levels, ordered=TRUE)
df_merged$rank_scam <- factor(df_merged$rank_scam, levels=rank_scam_levels, ordered=TRUE)

# income
df_merged$income <- factor(df_merged$income, ordered = TRUE, levels = income_levels)

# Binary binary_gender
df_merged$binary_gender <- factor(df_merged$gender, levels = c("Male", "Female"))
```

The following code creates data frames for adult and teen data separately (``df_merged_adult``` and ```df_merged_teen```).
```{r}
df_merged_adult <- df_merged %>% filter(adult == TRUE)
df_merged_teen <- df_merged %>% filter(adult == FALSE)
```

The following code defines the ```stat_test``` function. This function performs statistical testing between the variables listed in table 1 of the paper and the variable specified by the label in ```dep_var```. The function returns the results in the form of a data frame containing the name of the independent variable, the name of the dependent variable, the name of the test which was run, and the appropriate effect size measure. 

The parameters for the function are as follows: 

1. The parameter ```dep_var``` specifies the dependent variable which we want to test. If the column specified by ```dep_var``` is one of the possible independent variables, the test for that indepndent variable is skipped.

2. The variable ```condition_type``` specifies if the dependent variable should be tested based on which ```"legit"``` stimuli the participant saw or which ```"scam"``` stimuli the participant saw. For example, when testing for differences in participants' actions with respect to scam websites, it only makes sense to test for significant differences between the different scam stimuli shown. If no comparison based on condition is necessary, the ```test_condition``` variable can be set to FALSE. The default value for ```condition_type``` is ```"scam"``` and the default value for ```test_condition``` is ```TRUE```.

3. The parameter ```df``` specifies which dataframe should be used to perform the statistical test. The default value is ```df_merged```.

4. The variable ```stimuli_type``` specifies whether or not comparisons should be restricted to only participants who saw particular type of stimuli (i.e., Roblox or Spotify related). Setting the value to ```"roblox"``` will only perform statistical tests with participants who saw Roblox stimuli. Setting the value to ```"spotify"``` wil only perform statistical tests with participants who saw Spotify stimuli. The default value, ```"both"```, performs testing with the entire sample.

5. The variables ```fisher_B``` and ```fisher_simulate_p``` are passed through to the ```fisher.test``` parameters ```B``` and ```simulate.p.value```. These variables are used to enable simulating Fisher's test using a Monte Carlo simulation with 10,000 replications. This is necessary due to the computational in feasibility of running Fisher's test on some larger contingency tables. See the documentation of "fisher.test" for more details.

```{r}
stat_test <- function(dep_var, condition_type = "scam", df=df_merged, test_condition = TRUE, stimuli_tyoe = "both", fisher_B = 10000, fisher_simulate_p = TRUE, p.adjust.method = "BH") {
  raw_p = c()
  adjusted_p = c()
  indep_var_list = c()
  dep_var_list = c()
  test_list = c()
  effect_list = c()
  
  # Run fisher test dep_var v adult
  if(dep_var != "adult"){
    vs_adult <- fisher.test(table(df[[dep_var]], df$adult), B=fisher_B, simulate.p.value = fisher_simulate_p)
    raw_p = c(raw_p, vs_adult$p.value)
    indep_var_list = c(indep_var_list, "adult")
    dep_var_list = c(dep_var_list, dep_var)
    test_list = c(test_list, "fisher")
    effect_list = c(effect_list,cramer_v(table(df[[dep_var]], df$adult)))
  }
  # Run fisher test dep_var v  condition
  if(dep_var != "scam_condition" && dep_var != "legit_condition" && test_condition){
    if (condition_type == "scam"){
      vs_condition <- fisher.test(table(df[[dep_var]], df$scam_condition), B=fisher_B, simulate.p.value = fisher_simulate_p)
      indep_var_list = c(indep_var_list, "scam_condition")
      effect_list = c(effect_list,cramer_v(table(df[[dep_var]], df$scam_condition)))
    }else if (condition_type == "legit"){
      vs_condition <- fisher.test(table(df[[dep_var]], df$legit_condition), B=fisher_B, simulate.p.value = fisher_simulate_p)
      indep_var_list = c(indep_var_list, "legit_condition")
      effect_list = c(effect_list,cramer_v(table(df[[dep_var]], df$legit_condition)))
    }
    if (condition_type == "scam" || condition_type == "legit"){
      raw_p = c(raw_p, vs_condition$p.value)
      dep_var_list = c(dep_var_list, dep_var)
      test_list = c(test_list, "fisher")
    }
  }
  if (dep_var != "time_overall"){
    # Run fisher test dep_var v time_overall
    vs_time_overall <- CochranArmitageTest(table(df[[dep_var]], df$time_overall))
    raw_p = c(raw_p, vs_time_overall$p.value)
    indep_var_list = c(indep_var_list, "time_overall")
    dep_var_list = c(dep_var_list, dep_var)
    test_list = c(test_list, "CochranArmitageTest")
    effect_list = c(effect_list,freemanTheta(table(df[[dep_var]], df$time_overall)))
  }
  
  # Run fisher test dep_var v time_computer
  if(dep_var != "time_videos"){
    vs_time_videos <- CochranArmitageTest(table(df[[dep_var]], df$time_videos))
    raw_p = c(raw_p, vs_time_videos$p.value)
    indep_var_list = c(indep_var_list, "time_videos")
    dep_var_list = c(dep_var_list, dep_var)
    test_list = c(test_list, "CochranArmitageTest")
    effect_list = c(effect_list,freemanTheta(table(df[[dep_var]], df$time_videos)))
  }
  # Run fisher test dep_var v time_mobile
  if(dep_var != "time_mobile"){
    vs_time_mobile <- CochranArmitageTest(table(df[[dep_var]], df$time_mobile))
    raw_p = c(raw_p, vs_time_mobile$p.value)
    indep_var_list = c(indep_var_list, "time_mobile")
    dep_var_list = c(dep_var_list, dep_var)
    test_list = c(test_list, "CochranArmitageTest")
    effect_list = c(effect_list,freemanTheta(table(df[[dep_var]], df$time_mobile)))
  }
  
  # Run fisher test dep_var v time_computer
  if(dep_var != "time_computer"){
    vs_time_computer <- CochranArmitageTest(table(df[[dep_var]], df$time_computer))
    raw_p = c(raw_p, vs_time_computer$p.value)
    indep_var_list = c(indep_var_list, "time_computer")
    dep_var_list = c(dep_var_list, dep_var)
    test_list = c(test_list, "CochranArmitageTest")
    effect_list = c(effect_list,freemanTheta(table(df[[dep_var]], df$time_computer)))
  }
  # Run fisher test dep_var v time_social
  if(dep_var != "time_social"){
    vs_time_social <- CochranArmitageTest(table(df[[dep_var]], df$time_social))
    raw_p = c(raw_p, vs_time_social$p.value)
    indep_var_list = c(indep_var_list, "time_social")
    dep_var_list = c(dep_var_list, dep_var)
    test_list = c(test_list, "CochranArmitageTest")
    effect_list = c(effect_list,freemanTheta(table(df[[dep_var]], df$time_social)))
  }
  # Run fisher test dep_var v time_nonsocial
  if(dep_var != "time_nonsocial"){
    vs_time_nonsocial <- CochranArmitageTest(table(df[[dep_var]], df$time_nonsocial))
    raw_p = c(raw_p, vs_time_nonsocial$p.value)
    indep_var_list = c(indep_var_list, "time_nonsocial")
    dep_var_list = c(dep_var_list, dep_var)
    test_list = c(test_list, "CochranArmitageTest")
    effect_list = c(effect_list,freemanTheta(table(df[[dep_var]], df$time_nonsocial)))
  }
  # Run fisher test dep_var v risk_playedRoblox
  if(dep_var != "risk_playedRoblox" && (stimuli_tyoe == "both" || stimuli_tyoe == "roblox")){
    vs_risk_playedRoblox <- fisher.test(table(df[[dep_var]], df$risk_playedRoblox))
    raw_p = c(raw_p, vs_risk_playedRoblox$p.value)
    indep_var_list = c(indep_var_list, "risk_playedRoblox")
    dep_var_list = c(dep_var_list, dep_var)
    test_list = c(test_list,"CochranArmitageTest")
    effect_list = c(effect_list,freemanTheta(table(df[[dep_var]], df$risk_playedRoblox)))
  }
  # Run fisher test dep_var v risk_usedSpotify
  if(dep_var != "risk_usedSpotify" && (stimuli_tyoe == "both" || stimuli_tyoe == "spotify")){
    vs_risk_usedSpotify <- fisher.test(table(df[[dep_var]], df$risk_usedSpotify))
    raw_p = c(raw_p, vs_risk_usedSpotify$p.value)
    indep_var_list = c(indep_var_list, "risk_usedSpotify")
    dep_var_list = c(dep_var_list, dep_var)
    test_list = c(test_list,"CochranArmitageTest")
    effect_list = c(effect_list,freemanTheta(table(df[[dep_var]], df$risk_usedSpotify)))
  }
  # Run fisher test dep_var v risk_SpotifyPremium
  if(dep_var != "risk_spotifyPremium" && (stimuli_tyoe == "both" || stimuli_tyoe == "spotify")){
    vs_risk_purchased <- fisher.test(table(df[[dep_var]], df$risk_spotifyPremium), B=fisher_B, simulate.p.value = fisher_simulate_p)
    raw_p = c(raw_p, vs_risk_purchased$p.value)
    indep_var_list = c(indep_var_list, "risk_spotifyPremium")
    dep_var_list = c(dep_var_list, dep_var)
    test_list = c(test_list, "fisher")
    effect_list = c(effect_list,cramer_v(table(df[[dep_var]], df$risk_spotifyPremium)))
  }
  if(dep_var != "risk_puchasedRobux" && (stimuli_tyoe == "both" || stimuli_tyoe == "roblox")){
    vs_risk_purchased <- fisher.test(table(df[[dep_var]], df$risk_puchasedRobux), B=fisher_B, simulate.p.value = fisher_simulate_p)
    raw_p = c(raw_p, vs_risk_purchased$p.value)
    indep_var_list = c(indep_var_list, "risk_puchasedRobux")
    dep_var_list = c(dep_var_list, dep_var)
    test_list = c(test_list, "fisher")
    effect_list = c(effect_list,cramer_v(table(df[[dep_var]], df$risk_puchasedRobux)))
  }

  if(dep_var != "risk_freeSpotify" && (stimuli_tyoe == "both" || stimuli_tyoe == "spotify")){
    vs_risk_freePremium <- fisher.test(table(df[[dep_var]], df$risk_freeSpotify), B=fisher_B, simulate.p.value = fisher_simulate_p)
    raw_p = c(raw_p, vs_risk_freePremium$p.value)
    indep_var_list = c(indep_var_list, "risk_freeSpotify")
    dep_var_list = c(dep_var_list, dep_var)
    test_list = c(test_list, "fisher")
    effect_list = c(effect_list,cramer_v(table(df[[dep_var]], df$risk_freeSpotify)))
  }
  if(dep_var != "risk_freeRobux" && (stimuli_tyoe == "both" || stimuli_tyoe == "roblox")){
    vs_risk_freePremium <- fisher.test(table(df[[dep_var]], df$risk_freeRobux), B=fisher_B, simulate.p.value = fisher_simulate_p)
    raw_p = c(raw_p, vs_risk_freePremium$p.value)
    indep_var_list = c(indep_var_list, "risk_freeRobux")
    dep_var_list = c(dep_var_list, dep_var)
    test_list = c(test_list, "fisher")
    effect_list = c(effect_list,cramer_v(table(df[[dep_var]], df$risk_freeRobux)))
  }
  # Run fisher test dep_var v risk_noRefund
  if(dep_var != "risk_noRefund"){
    vs_risk_noRefund <- CochranArmitageTest(table(df[[dep_var]], df$risk_noRefund))
    raw_p = c(raw_p, vs_risk_noRefund$p.value)
    indep_var_list = c(indep_var_list, "risk_noRefund")
    dep_var_list = c(dep_var_list, dep_var)
    test_list = c(test_list, "CochranArmitageTest")
    effect_list = c(effect_list,freemanTheta(table(df[[dep_var]], df$risk_noRefund)))
  }
  # Run fisher test dep_var v risk_onlineTasks
  if(dep_var != "risk_onlineTasks"){
    vs_risk_onlineTasks <- CochranArmitageTest(table(df[[dep_var]], df$risk_onlineTasks))
    raw_p = c(raw_p, vs_risk_onlineTasks$p.value)
    indep_var_list = c(indep_var_list, "risk_onlineTasks")
    dep_var_list = c(dep_var_list, dep_var)
    test_list = c(test_list, "CochranArmitageTest")
    effect_list = c(effect_list,freemanTheta(table(df[[dep_var]], df$risk_onlineTasks)))
  }
  # Run fisher test dep_var v risk_crypto
  if(dep_var != "risk_crypto"){
    vs_risk_crypto <- CochranArmitageTest(table(df[[dep_var]], df$risk_crypto))
    raw_p = c(raw_p, vs_risk_crypto$p.value)
    indep_var_list = c(indep_var_list, "risk_crypto")
    dep_var_list = c(dep_var_list, dep_var)
    test_list = c(test_list, "CochranArmitageTest")
    effect_list = c(effect_list,freemanTheta(table(df[[dep_var]], df$risk_crypto)))
  }
  # Run fisher test dep_var v often_onlinetask
  if(dep_var != "often_onlinetask"){
    vs_often_onlinetask <- CochranArmitageTest(table(df[[dep_var]], df$often_onlinetask))
    raw_p = c(raw_p, vs_often_onlinetask$p.value)
    indep_var_list = c(indep_var_list, "often_onlinetask")
    dep_var_list = c(dep_var_list, dep_var)
    test_list = c(test_list, "CochranArmitageTest")
    effect_list = c(effect_list,freemanTheta(table(df[[dep_var]], df$often_onlinetask)))
  }
  # Run fisher test dep_var v income
  if(dep_var != "income"){
    vs_income <- CochranArmitageTest(table(df[[dep_var]], df$income))
    raw_p = c(raw_p, vs_income$p.value)
    indep_var_list = c(indep_var_list, "income")
    dep_var_list = c(dep_var_list, dep_var)
    test_list = c(test_list, "CochranArmitageTest")
    effect_list = c(effect_list,freemanTheta(table(df[[dep_var]], df$income)))
  }
  # Run fisher test dep_var v binary_gender
  if(dep_var != "binary_gender"){
    vs_binary_gender <- fisher.test(table(df[[dep_var]], df$binary_gender), B=fisher_B, simulate.p.value = fisher_simulate_p)
    raw_p = c(raw_p, vs_binary_gender$p.value)
    indep_var_list = c(indep_var_list, "binary_gender")
    dep_var_list = c(dep_var_list, dep_var)
    test_list = c(test_list, "fisher")
    effect_list = c(effect_list,cramer_v(table(df[[dep_var]], df$binary_gender)))
  }
  # Run fisher test dep_var v community_type
  if(dep_var != "community_type"){
    vs_community_type <- fisher.test(table(df[[dep_var]], df$community_type), B=fisher_B, simulate.p.value = fisher_simulate_p)
    raw_p = c(raw_p, vs_community_type$p.value)
    indep_var_list = c(indep_var_list, "community_type")
    dep_var_list = c(dep_var_list, dep_var)
    test_list = c(test_list, "fisher")
    effect_list = c(effect_list,cramer_v(table(df[[dep_var]], df$community_type)))
  }
  # adjust p values
  adjusted_p = p.adjust(raw_p, method = p.adjust.method)
  
  # compute significant results
  significant_list = c()
  for(i in adjusted_p){
    if (i < 0.05){
      significant_list = c(significant_list, TRUE)
    }else{
      significant_list = c(significant_list, FALSE)
    }
  }
  # return
  output_df = data.frame(independent=indep_var_list, dependent=dep_var_list, test=test_list, p.adjusted=adjusted_p, p.raw = raw_p, effect_size = effect_list, significant = significant_list)
  return(output_df)
}
```


## Descriptive statistics

The following code blocks produce tables describing the gender, community type, state, household income, and age for the entire sample and the teen/adult samples independently. 

```{r}
print("Overall gender distribution")
prop.table(table(df_merged$gender, useNA = "always"))
print("Adult gender distribution")
prop.table(table(df_merged_adult$gender, useNA = "always"))
print("Teen gender distribution")
prop.table(table(df_merged_teen$gender, useNA = "always"))
```

```{r}
print("Overall community type distribution")
prop.table(table(df_merged$community_type, useNA = "always"))
print("Adult community type distribution")
prop.table(table(df_merged_adult$community_type, useNA = "always"))
print("Teen community type distribution")
prop.table(table(df_merged_teen$community_type, useNA = "always"))
```

```{r}
print("Overall state distribution")
sort(prop.table(table(df_merged$state, useNA = "always")))
print("Adult state distribution")
sort(prop.table(table(df_merged_adult$state, useNA = "always")))
print("Teen state distribution")
sort(prop.table(table(df_merged_teen$state, useNA = "always")))
```

```{r}
print("Overall income distribution")
prop.table(table(df_merged$income, useNA = "always"))
print("Adult income distribution")
prop.table(table(df_merged_adult$income, useNA = "always"))
print("Teen income distribution")
prop.table(table(df_merged_teen$income, useNA = "always"))
```

```{r}
df_merged_adult <- df_merged_adult %>% mutate(age_cat = case_when(
                         age >= 18 & age <= 24 ~ "18 to 24",
                         age >= 25 & age <= 34 ~ "25 to 34", 
                         age >= 35 & age <= 44 ~ "35 to 44",
                         age >= 45 & age <= 54 ~ "45 to 54",
                         age >= 55 ~ "55+",
                         TRUE ~ NA_character_))
print("Adult age distribution")
prop.table(table(df_merged_adult$age_cat))

print("Teen age distribution")
prop.table(table(df_merged_teen$age))

```

The following code blocks produce tables describing the various aspects of behavior asked about at the beginning of the survey for the entire sample and the teen/adult samples independently.  This includes devices used in the last week, social media services used in the last week, hours per day spent on digital entertainment, etc.

```{r}
# unlist(str_split(*)) splits comma separated values
print("Overall social media services used in the last week distribution")
table(unlist(str_split(df_merged$social_media, ",")))/nrow(df_merged)
print("Teens social media services used in the last week distribution")
table(unlist(str_split(df_merged_teen$social_media, ",")))/nrow(df_merged_teen)
print("Adults social media services used in the last week distribution ")
table(unlist(str_split(df_merged_adult$social_media, ",")))/nrow(df_merged_adult)
```
```{r}
print("Overall devices used in the last week distribution")
table(trimws(unlist(str_split(df_merged$devices, ","))))/nrow(df_merged)
print("Teens devices used in the last week distribution")
table(trimws(unlist(str_split(df_merged_teen$devices, ","))))/nrow(df_merged_teen)
print("Adults devices used in the last week distribution")
table(trimws(unlist(str_split(df_merged_adult$devices, ","))))/nrow(df_merged_adult)

```

```{r}
print("Overall distribution of hours per day on digital entertainment")
prop.table(table(df_merged$time_overall, useNA = "always"))
print("Adult distribution of hours per day on digital entertainment")
prop.table(table(df_merged_adult$time_overall, useNA = "always"))
print("Teen distribution of hours per day on digital entertainment")
prop.table(table(df_merged_teen$time_overall, useNA = "always"))
```
```{r}
print("Overall distribution of time on watching online videos per week")
prop.table(table(df_merged$time_videos, useNA = "always"))
print("Adult distribution of time on watching online videos per week")
prop.table(table(df_merged_adult$time_videos, useNA = "always"))
print("Teen distribution of time on watching online videos per week")
prop.table(table(df_merged_teen$time_videos, useNA = "always"))

```

```{r}
print("Overall distribution of frequency of playing robux")
prop.table(table(df_merged$risk_playedRoblox))
print("Adult distribution of frequency of playing robux")
prop.table(table(df_merged_adult$risk_playedRoblox))
print("Teen distribution of frequency of playing robux")
prop.table(table(df_merged_teen$risk_playedRoblox))
```
```{r}
print("Overall distribution of frequency of using Spotify")
prop.table(table(df_merged$risk_usedSpotify))
print("Adult distribution of frequency of using Spotify")
prop.table(table(df_merged_adult$risk_usedSpotify))
print("Teen distribution of frequency of using Spotify")
prop.table(table(df_merged_teen$risk_usedSpotify))

```


## Statistical testing
### Adult vs Teen comparisons
The following code tests which potential independent variables are associated with whether a participant is a teen or an adult
```{r}
adult_results <- stat_test(dep_var ="adult", condition_type = "scam")
```

**Paper Result**: The following code prints results that are significantly associated with being an adult/teen. These results are discussed in section 5A of the paper
```{r}
adult_results %>% filter(significant == TRUE)
```
The following code prints cross tabs for significant variables. Each row represents either Teens or Adults.  Each column represents a value of the tested variable. For the rows: 0 = teens, 1 = adults.
```{r}
print("Age vs.  Frequency of use of Roblox")
print(prop.table(table(df_merged$adult, df_merged$risk_playedRoblox),1))
```

```{r}
print("Age vs. Freuqnecy of use of Spotify")
print(prop.table(table(df_merged$adult, df_merged$risk_usedSpotify),1))
```
```{r}
print("Age vs. Purchased Roblox")
print(prop.table(table(df_merged$adult, df_merged$risk_puchasedRobux),1))
```
```{r}
print("Age vs. Frequency of playing mobile phone games")
prop.table(table(df_merged$adult, df_merged$time_mobile),1) 
```

```{r}
print("Age vs. Frequency of shopping with no refund")
prop.table(table(df_merged$adult, df_merged$risk_noRefund),1) 
```
```{r}
print("Age vs. Frequency of doing online tasks for money")
prop.table(table(df_merged$adult, df_merged$risk_onlineTasks),1)
```

```{r}
print("Age vs. Frequency of online tasks for money without being paid")
prop.table(table(df_merged$adult, df_merged$often_onlinetask),1)
```
```{r}
print("Age vs. Frequency of purchasing crypto assets")
prop.table(table(df_merged$adult, df_merged$risk_crypto),1) 
```

```{r}
# income
print("Age vs. Household Income")
prop.table(table(df_merged$adult, df_merged$income, useNA = "always"),1) 
```
### Gender comparisons

The following code tests which potential independent variables are associated with binary gender. Sample size was insufficient to include non-binary individuals in this analysis. These comparisons are post-hoc.
```{r}
binary_gender_results <- stat_test(dep_var ="binary_gender", condition_type = "scam")
```

**Paper Result**: The following code prints results that are significantly associated with binary gender These results are discussed in section 5D of the paper
```{r}
binary_gender_results %>% filter(significant == TRUE)
```
The following code prints cross tabs for significant variables. Each row represents either men or women.  Each column represents a value of the tested variable. 
```{r}
print("Gender vs.Time spent on digital entertainment")
prop.table(table(df_merged$binary_gender, df_merged$time_overall))
```
```{r}
print("Gender vs.Time spent watching online videos per week")
prop.table(table(df_merged$binary_gender, df_merged$time_videos), 1)
```


```{r}
print("Gender vs.Time spent on computer/console games")
prop.table(table(df_merged$binary_gender, df_merged$time_computer),1)
```

```{r}
print("Gender vs.time spent on non-social media websites per week")
prop.table(table(df_merged$binary_gender, df_merged$time_nonsocial), 1)
```

```{r}
print("Gender vs.Frequency of purchasing crypto assets")
prop.table(table(df_merged$binary_gender, df_merged$risk_crypto), 1)
```
### Experience searching for Free Robux comparisons
The following code tests which potential independent variables are significantly associated with experience searching for "Free Roblox robux" or something similar

```{r}
roblox_s_results <- stat_test("roblox_s", stimuli_tyoe = "roblox",condition_type = "neither")
```
**Paper Result**: The following code prints results for variables that are significantly associated with experience previously searching for "Free Roblox robux" or something similar. These results are discussed in section 5C and 5D of the paper.
```{r}
roblox_s_results %>% filter(significant == TRUE,)
```
The following code prints cross tabs for significant variables. Each row represents people reported previously searching for "Free Roblox robux" or something similar vs. those who had not searched. 0 = those who had not searched, 1 = those who had searched. 

```{r}
print("Searching for Free Robux vs. Age")
prop.table(table(df_merged$adult, df_merged$roblox_s),1)
```
```{r}
print("Searching for Free Robux vs.Frequency of playing Roblox")
table(df_merged$roblox_s, df_merged$risk_playedRoblox)
# two times or fewer: 108 total, 9 say they searched = 9/108 = 8.3%
# Three times or more: 32 total, 14 say they searched 14/32 = 0.4375 
```

```{r}
print("Searching for Free Robux vs.Purchasing Robux")
prop.table(table(df_merged$roblox_s, df_merged$risk_puchasedRobux),2)
```

```{r}
print("Searching for Free Robux vs.Receiving Free Robux ")
prop.table(table(df_merged$roblox_s, df_merged$risk_freeRobux ),2)
```
```{r}
print("Searching for Free Robux vs.Frequency of doing online tasks")
prop.table(table(df_merged$roblox_s, df_merged$risk_onlineTasks ),2)
```

### Experience searching for Free Spotify comparisons
The following code tests which potential independent variables are significantly associated with previously searching for "Free Spotify Premium" or something similar.
```{r}
spotify_s_results <- stat_test("spotify_s", stimuli_tyoe = "spotify", condition_type = "neither")
```
**Paper Result**: The following code shows that none of the tested variables varied significantly 
```{r}
spotify_s_results %>% filter(significant == TRUE)
```

### Free Robux search liklihood comparisons
The following code tests which potential independent variables are significantly associated with a liklihood of  searching for "Free Roblox Robux" or something similar

```{r}
# Bin to likely vs unlikely
df_merged <- df_merged %>% mutate(rbolox_s_likleihood_bool = ifelse(roblox_s_likliehood == "Somewhat likely", TRUE,ifelse(roblox_s_likliehood == "Extremely likely", TRUE, ifelse(is.na(roblox_s_likliehood), NA, FALSE))))
roblox_s_likliehood_results <- stat_test("rbolox_s_likleihood_bool", stimuli_tyoe = "roblox")
```
The following code shows that none of the tested variables varied significantly 
```{r}
roblox_s_likliehood_results %>% filter(significant == TRUE)
```

### Free Spotify search liklihood comparisons
The following code tests which potential independent variables are significantly associated with a likelihood of  searching for "Free Spotify Premium" or something similar
```{r}
# Bin to likely vs unlikely
df_merged <- df_merged %>% mutate(spotify_s_liklihood_bool = ifelse(spotify_s_liklihood == "Somewhat likely", TRUE,ifelse(spotify_s_liklihood == "Extremely likely", TRUE, ifelse(is.na(spotify_s_liklihood), NA, FALSE))))
spotify_s_liklihood_results <- stat_test("spotify_s_liklihood_bool", stimuli_tyoe = "spotify")
```
The following code shows that none of the tested variables varied significantly 
```{r}
spotify_s_liklihood_results %>% filter(significant == TRUE)
```



### Scam Ranking comparions
The following code tests which potential independent variables  are significantly associated with correctly identifying the scam stimuli
```{r}
rank_scam_results <- stat_test(dep_var ="rank_scam_bool", condition_type = "scam")
```
**Paper Result**: The following code prints results for variables that are significantly associated with correctly identifying scam stimuli. These results are discussed in section 5D 
```{r}
rank_scam_results %>% filter(significant == TRUE)
```

The following code prints cross tables for significant results. The rows represent whether or not scam video was correctly identified. 0 = participant identified the video as legit or selected I don't know, 1 = participant identified the video as a scam. 

```{r}
print("Correct scam identification vs. stimuli shown")
prop.table(table(df_merged$rank_scam_bool, df_merged$scam_condition), 2)
print("Scam ranking vs. stimuli shown")
prop.table(table(df_merged$rank_scam, df_merged$scam_condition ),2)
```
```{r}
print("Correct scam identification vs. gender")
prop.table(table(df_merged$rank_scam_bool, df_merged$binary_gender), 2)
print("Scam ranking vs. gender")
table(df_merged$rank_scam, df_merged$binary_gender)
# 29 women did not identify scam. 13 of these selected I'm not sure. 13/29 = 0.4482759
# 9 men did not identify scam. 3 of these selected I'm not sure. 3/9 = 0.333333
```

```{r}
print("Correct scam identification vs. time on computer/console games")
prop.table(table(df_merged$time_computer, df_merged$rank_scam_bool),1)
```


#### Post-hoc comparisons
**Paper Result** Gender is associated with amount of time spent daily on digital entertainment activities. The following code tests whether time spent on digital entertainment activities is a significant predictor of ranking success when controlling for gender. From this, we see that time remains a weakly significant predictor for women ($p_{uncorrected} < 0.006$, $\theta = 0.181$) but not men ($p_{uncorrected} = 0.156$)
```{r}
# bin to men and women separately
df_merged_men <- df_merged %>% filter(binary_gender == "Male")
df_merged_women <- df_merged %>% filter(binary_gender == "Female")
print("Test scam ranking vs. time overall with just men")
CochranArmitageTest(table(df_merged_men$time_overall, df_merged_men$rank_scam_bool))
print("Test scam ranking vs. time overall with just women")
CochranArmitageTest(table(df_merged_women$time_overall, df_merged_women$rank_scam_bool))
freemanTheta(table(df_merged_women$time_overall, df_merged_women$rank_scam_bool))
```

**Paper Result** Gender is associated with amount of time spent weekly on console/computer games. The following code tests whether time spent on console/comptuer games is a significant predictor of ranking success when controlling for gender. From this, we see that time remains a not a significant predictor for just women ($p_{uncorrected} = 0.159$) or just men($p_{uncorrected} = 0.275$)
```{r}
# Check if difference exists with just men
print("Test scam ranking vs. time on console/computer games with just men")
CochranArmitageTest(table(df_merged_men$time_computer, df_merged_men$rank_scam_bool))
print("Test scam ranking vs. time on console/computer games with just women")
CochranArmitageTest(table(df_merged_women$time_computer, df_merged_women$rank_scam_bool))
```


### Legit Ranking comparions
The following code tests which potential independent variables are significantly associated with correctly identifying the legit stimuli
```{r}
rank_legit_results <- stat_test(dep_var ="rank_legit_bool", condition_type = "legit")
```

The following code prints results for variables that are significantly associated with correctly identifying legit stimuli
```{r}
rank_legit_results %>% filter(significant == TRUE)
```
The following code prints cross tables for significant results. The rows represent whether or not legit video was correctly identified. 0 = participant identified the video as a scam or selected I don't know, 1 = participant identified the video as legit. 
```{r}
print("Correct legit identification vs. legit stimuli shown")
prop.table(table(df_merged$rank_legit_bool,df_merged$legit_condition),2)
print("Legit ranking vs. legit stimuli shown")
prop.table(table(df_merged$rank_legit,df_merged$legit_condition),2)
```

```{r}
print("Correct legit identification vs. frequency of doing online tasks")
prop.table(table(df_merged$rank_legit_bool, df_merged$risk_onlineTasks), 2)
print("Legit ranking vs. frequency of doing online tasks")
prop.table(table(df_merged$rank_legit, df_merged$risk_onlineTasks), 2)
```

### Legit action comparisons
#### Legit Youtube video comparisons
The following code splits the list of actions that the user recommended in response to the legit youtube videos into columns of booleans, with each boolean indicating whether or not an action was selected.For example, ```Exit.the.video.without.doing.anything``` is ```TRUE``` if the partiicpant recommended that their friend exit the video. 
```{r}
splitup <- sapply(unlist(df_merged$legit), strsplit, ',')
headnames <- unique(unlist(splitup))
mat <- t(unname(sapply(splitup, function(x) headnames %in% x)))
colnames(mat) <- headnames
df_legit_actions <- data.frame(df_merged, mat)
```

Each of the following subsections runs the statistical testing for a particular action.

##### Exit 
The following code tests which potential independent variables are significantly associated with recommending exiting the legit YouTube video.
```{r}
legit_exit_results <- stat_test(dep_var = "Exit.the.video.without.doing.anything", df=df_legit_actions, condition_type = "legit")
```
**Paper Result**: The following code prints results for variables that are significantly associated with recommending to Exit the legit YouTube video. The fact that legit stimuli shown is significantly associated with the rate of exiting the legit YouTube video is presented in Figure 3a of the paper. 
```{r}
legit_exit_results %>% filter(significant == TRUE)
```
The following code prints the rate of recommending to exit the legit YouTube video by legit stimuli shown 
```{r}
prop.table(table(df_legit_actions$Exit.the.video.without.doing.anything, df_legit_actions$legit_condition),2)
```
##### Search to learn more
The following code tests which potential independent variables are significantly associated with recommending searching to learn more about the legit YouTube video.
```{r}
legit_search_results <- stat_test(dep_var = "Search.online.to.learn.more.about.what.the.video.describes", df=df_legit_actions, condition_type = "legit")
```
**Paper Result**: The following code prints results for variables that are significantly associated with recommending to search for more information about the legit YouTube video. The fact that legit stimuli shown is significantly associated the rate of searching for more information about the legit YouTube video is presented in Figure 3a of the paper. 
```{r}
legit_search_results %>% filter(significant == TRUE)
```
The following code prints the rate of recommending to search to learn more about the legit YouTube video by legit stimuli shown. 
```{r}
prop.table(table(df_legit_actions$Search.online.to.learn.more.about.what.the.video.describes, df_legit_actions$legit_condition),2)
```
##### Report the video
The following code tests which potential independent variables are significantly associated with recommending to report the legit YouTube video.
```{r}
legit_report_results <- stat_test(dep_var = "Report.the.video.to.YouTube", df=df_legit_actions, condition_type = "legit")
```
**Paper Result**: The following code prints results for variables that are significantly associated with recommending to report the legit YouTube video. This result is discussed in section 5D of the paper. 
```{r}
legit_report_results %>% filter(significant == TRUE)
```
The following code prints the rate of recommending to report the legit YouTube video by frequency of doing online tasks. 
```{r}
prop.table(table(df_legit_actions$Report.the.video.to.YouTube, df_legit_actions$risk_onlineTasks),2)
```
###### Post-hoc result
**Paper Result** Being an adult/teen is associated with frequency of doing online tasks. While being an adult/teen was not found to be a significant predictor of reporting legit YouTube videos, it was a significant predictor for reporting scam YouTube videos. For this reason, the following code tests whether frequency of doing online tasks  is a significant predictor of ranking success when controlling for age. From this, we see that frequency of online tasks is not a significant predictor when looking at adults ($p_{uncorrected} = 0.1049$) or teens alone ($p_{uncorrected} = 0.4185$) This result is discussed in section 5D of the paper. 
```{r}
df_legit_actions_adult<-df_legit_actions %>% filter(adult == TRUE)
df_legit_actions_teen<-df_legit_actions %>% filter(adult == FALSE)
print("Test reporting legit YouTube videos vs. frequency of doing online tasks with just adults")
CochranArmitageTest(table(df_legit_actions_adult$risk_onlineTasks, df_legit_actions_adult$Report.the.video.to.YouTube))
print("Test reporting legit YouTube videos vs. frequency of doing online tasks with just teens")
CochranArmitageTest(table(df_legit_actions_teen$risk_onlineTasks, df_legit_actions_teen$Report.the.video.to.YouTube))
```

##### Visit the website
The following code tests which potential independent variables are significantly associated with recommending to visit the website from the legit YouTube video.
```{r}
legit_visit_results <- stat_test(dep_var = "Visit.the.website.s..shown.in.the.video", df=df_legit_actions, condition_type = "legit")
```
**Paper Result**: The following code prints results for variables that are significantly associated with recommending to visit the website shown in legit YouTube video. 
The fact that legit stimuli shown is significantly associated the rate of vising the website shown in the legit YouTube video is presented in Figure 3a of the paper. The other results are not discussed due to a lack of space. 
```{r}
legit_visit_results %>% filter(significant == TRUE)
```
The following code prints cross tables for significant results. The rows represent whether or not the user recommended visiting the website shown in the legit YouTube video. 
```{r}
print("Visit legit website vs. teen (0)/adult(1)")
prop.table(table(df_legit_actions$Visit.the.website.s..shown.in.the.video, df_legit_actions$adult),2)

```
```{r}
print("Visit legit website vs. legit stimuli shown")
prop.table(table(df_legit_actions$Visit.the.website.s..shown.in.the.video, df_legit_actions$legit_condition),2)
```

```{r}
print("Visit legit website vs. time spent playing mobile games")
prop.table(table(df_legit_actions$time_mobile, df_legit_actions$Visit.the.website.s..shown.in.the.video),1)
```

```{r}
print("online tasks vs visit website")
prop.table(table(df_legit_actions$risk_onlineTasks, df_legit_actions$Visit.the.website.s..shown.in.the.video),1)
```

###### Post-hoc tests
Being an adult/teen is associated with time spent playing mobile games per week. The following code determines whether time spent playing mobile games remains a significant predictor when controlling for age. From this, we see that time spent on mobile games remains a significant predictor of visiting the website shown in the legit YouTube video, even when looking at just adults ($p_{uncorrected} = 0.014$) or teens ($p_{uncorrected} < 0.001$).
```{r}
df_legit_actions_adult<-df_legit_actions %>% filter(adult == TRUE)
df_legit_actions_teen<-df_legit_actions %>% filter(adult == FALSE)
print("Test visit website vs. time on mobile games with just adults")
CochranArmitageTest(table(df_legit_actions_adult$time_mobile, df_legit_actions_adult$Visit.the.website.s..shown.in.the.video))
print("Test visit website vs. time on mobile games with just teens")
CochranArmitageTest(table(df_legit_actions_teen$time_mobile, df_legit_actions_teen$Visit.the.website.s..shown.in.the.video))
```

Being an adult/teen is associated with frequency of doing online tasks. The following code determines whether frequency of doing online tasks remains a significant predictor when controlling for age. From this, we see that frequency of doing online tasks remains weakly significant predictor of visiting the website shown in the legit YouTube video only for teens alone ($p_{uncorrected} = 0.012$), but not adults alone ($p_{uncorrected} = 0.4441$)
```{r}
print("online tasks vs visit website for adults")
CochranArmitageTest(table(df_legit_actions_adult$risk_onlineTasks, df_legit_actions_adult$Visit.the.website.s..shown.in.the.video))
print("online tasks vs visit website for teens")
CochranArmitageTest(table(df_legit_actions_teen$risk_onlineTasks, df_legit_actions_teen$Visit.the.website.s..shown.in.the.video))
```

##### Look at the comments
The following code tests which potential independent variables are significantly associated with recommending to look at the comments on the legit YouTube video.
```{r}
legit_lookatcomments_results <- stat_test(dep_var = "Look.at.the.comments.on.the.video", df=df_legit_actions, condition_type = "legit")
```
The following code shows that none of the tested variables were significantly associated with looking at the comments on the legit YouTube video
```{r}
legit_lookatcomments_results %>% filter(significant == TRUE)
```
##### Leave a comment
The following code tests which potential independent variables are significantly associated with recommending to leave a comment on the legit YouTube video
```{r}
legit_leaveacomment_results <- stat_test(dep_var = "Leave.a.comment.on.the.video..please.specify.", df=df_legit_actions, condition_type = "legit")
```
The following code shows that none of the tested variables were significantly associated with recommending to leave a comment on the legit YouTube video
```{r}
legit_leaveacomment_results %>% filter(significant == TRUE)
```
##### other
The following code tests which potential independent variables are significantly associated with recommending a different action in response to the legit YouTube video
```{r}
legit_other_results <- stat_test(dep_var = "Other..please.specify.", df=df_legit_actions, condition_type = "legit")
```
The following code shows that none of the tested variables were significantly associated with recommending a different action in response to the legit YouTube video
```{r}
legit_other_results %>% filter(significant == TRUE)
```

#### Legit Web video cmpariosons
The following code splits the list of actions that the user recommended in response to the legit website videos into columns of booleans, with each boolean indicating whether or not an action was selected.For example, ```Exit.from.the.website.without.doing.anything``` is ```TRUE``` if the partiicpant recommended that their friend exit the website. 
```{r}
splitup <- sapply(unlist(df_merged$lgt_web), strsplit, ',')
headnames <- unique(unlist(splitup))
mat <- t(unname(sapply(splitup, function(x) headnames %in% x)))
colnames(mat) <- headnames
df_lgt_web_actions <- data.frame(df_merged, mat)
```

##### Exit
The following code tests which potential independent variables are significantly associated with recommending to exit the legit website
```{r}
lgt_web_exit_results <- stat_test(dep_var = "Exit.from.the.website.without.doing.anything", df=df_lgt_web_actions, condition_type = "legit")
```
The following code shows that none of the tested variables were significantly associated with exiting the legit website.
```{r}
lgt_web_exit_results %>% filter(significant == TRUE)
```


##### Search online
The following code tests which potential independent variables are significantly associated with recommending to search to learn more about the legit website
```{r}
lgt_web_search_results <- stat_test(dep_var = "Search.online.to.learn.more.about.the.website", df=df_lgt_web_actions, condition_type = "legit")
```
The following code prints results for variables that are significantly associated with recommending to search to learn more about the legit website.
```{r}
lgt_web_search_results %>% filter(significant == TRUE)
```
The following code prints the table comparing the rate of recommending to search to learn more about the legit website based on level of usage of Spotify
```{r}
prop.table(table(df_lgt_web_actions$Search.online.to.learn.more.about.the.website, df_lgt_web_actions$risk_usedSpotify),2)
```

##### Follow all instructions
The following code tests which potential independent variables are significantly associated with recommending to follow the instructions from the legit video.
```{r}
lgt_web_follow_results <- stat_test(dep_var = "Follow.all.of.the.instructions.in.the.video.to.complete.the.offer", df=df_lgt_web_actions, condition_type = "legit")
```
The following code shows that none of the tested variables were significantly associated with following the instrucitons on the legit website.
```{r}
lgt_web_follow_results %>% filter(significant == TRUE)
```


##### Register for website
The following code tests which potential independent variables are significantly associated with recommending to register for the legit video.
```{r}
lgt_web_register_results <- stat_test(dep_var = "Register.for.the.website", df=df_lgt_web_actions, condition_type = "legit")
```
**Paper result**: The following code prints results for variables that are significantly associated with recommending to register for the legit website. The fact that legit stimuli is significantly associated with recommending to register for the website is shown in figure 3b. 
```{r}
lgt_web_register_results %>% filter(significant == TRUE)
```
The following code prints cross tables for significant results. The rows represent whether or not the user recommended visiting the website shown in the legit YouTube video. 
```{r}
print("Register for the legit website vs legit stimuli shown ")
prop.table(table(df_lgt_web_actions$Register.for.the.website, df_lgt_web_actions$legit_condition),2)
```
```{r}
print("Rgister for legit website vs. rate of doing online tasks")
prop.table(table(df_lgt_web_actions$Register.for.the.website, df_lgt_web_actions$risk_onlineTasks),2)
```

##### Ask for help
The following code combines the option presented to adults ("Ask a knowledgeable friend for help") with the option presented ot teens ("Ask a parent for help")
```{r}
df_lgt_web_actions$Ask.for.help <- df_lgt_web_actions$Ask.a.knowledgeable.friend.for.help | df_lgt_web_actions$Ask.a.parent.for.help
```
The following code tests which potential independent variables are significantly associated with recommending to ask for help when viewing the legit website
```{r}
lgt_web_ask_for_help_results <- stat_test(dep_var = "Ask.for.help", df=df_lgt_web_actions, condition_type = "legit")
```
**Paper result**: The following code prints results for variables that are significantly associated with asking for help when viewing the legit website. The fact that teens were more likely to recommend asking for hlep is discussed in seciton 5C
```{r}
lgt_web_ask_for_help_results %>% filter(significant == TRUE)
```
The following code prints the rate of recommending asking for help between teens (0) and adults (1). The rows represent recommending asking for help or not. 
```{r}
prop.table(table(df_lgt_web_actions$Ask.for.help, df_lgt_web_actions$adult),2)
```

##### Other
The following code tests which potential independent variables are significantly associated with recommending another action when viewing the legit website
```{r}
lgt_other_results <- stat_test(dep_var = "Other..please.specify.", df=df_lgt_web_actions)
```
The following code shows that none of the tested variables were significantly associated with recommending another action when viewing the legit website.
```{r}
lgt_other_results %>% filter(significant == TRUE)
```

### Scam action comparsons
#### Scam YouTube video comparisons
The following code splits the list of actions that the user recommended in response to the legit YouTube videos into columns of booleans, with each boolean indicating whether or not an action was selected.For example, ```Exit.the.video.without.doing.anything``` is ```TRUE``` if the participant recommended that their friend exit the video. 
```{r}
splitup <- sapply(unlist(df_merged$scam), strsplit, ',')
headnames <- unique(unlist(splitup))
mat <- t(unname(sapply(splitup, function(x) headnames %in% x)))
colnames(mat) <- headnames
df_scam_actions <- data.frame(df_merged, mat)
```


**Paper result**: The following code calculates the proportion of participants who both recommended visiting the scam website alongside another information gathering action. These proportions are discussed in section 5B of the paper. 
```{r}
print("Proportion of participants who recommended to visit the website AND look at the comments")
nrow(filter(df_scam_actions, Visit.the.website.s..shown.in.the.video &  (Look.at.the.comments.on.the.video)))/nrow(filter(df_scam_actions, Visit.the.website.s..shown.in.the.video))
print("Proportion of participants who recommended to visit the website AND search online to learn more")
nrow(filter(df_scam_actions, Visit.the.website.s..shown.in.the.video &  (Search.online.to.learn.more.about.what.the.video.describes)))/nrow(filter(df_scam_actions, Visit.the.website.s..shown.in.the.video))
```

##### Exit 
The following code tests which potential independent variables are significantly associated with recommending exiting the scam YouTube video.
```{r}
scam_exit_results <- stat_test(dep_var = "Exit.the.video.without.doing.anything", df=df_scam_actions)
```
The following code shows that none of the tested independent variables are significantly associated with recommending to exit the scam YouTube video. 
```{r}
scam_exit_results %>% filter(significant == TRUE)
```

##### Search to learn more
The following code tests which potential independent variables are significantly associated with recommending searching to learn more about the scam YouTube video.
```{r}
scam_search_results <- stat_test(dep_var = "Search.online.to.learn.more.about.what.the.video.describes", df=df_scam_actions)
```
**Paper result**: The following code prints results for variables that are significantly associated with recommending to search to learn more about the scam YouTube video. The fact that searching to learn more about the scam YouTube is significantly associated with scam stimuli is shown in figure 2a
```{r}
scam_search_results %>% filter(significant == TRUE)
```   
The following code prints the rate of recommending to search to learn more about the scam YouTube video by stimuli shown. The rows represent whether the partiicpant recommended to search to learn more or not.
```{r}
prop.table(table(df_scam_actions$Search.online.to.learn.more.about.what.the.video.describes, df_scam_actions$scam_condition ),2)
```

##### Report the video
The following code tests which potential independent variables are significantly associated with recommending to report the scam YouTube video.
```{r}
scam_report_results <- stat_test(dep_var = "Report.the.video.to.YouTube", df=df_scam_actions)
```

**Paper result**: The following code prints results for variables that are significantly associated with recommending to report the scam YouTube video. The fact that the rate of recommending to report the scam YouTube video significantly associated with being a teen/adult is discussed in section 5C. The fact that the frequency of doing online tasks was (probably spuriously) associated with the rate of reporting videos is discussed in section 5D.
```{r}
scam_report_results %>% filter(significant == TRUE)
```  
The following code prints cross tables for significant results. The rows represent whether or not the user recommended reporting the scam YouTube video.

```{r}
print("Report scam video vs. teen (0)/adult(1) ")
prop.table(table(df_scam_actions$Report.the.video.to.YouTube, df_scam_actions$adult),2)
```
```{r}
print("Report scam video vs. frequency of doing online tasks")
prop.table(table(df_scam_actions$Report.the.video.to.YouTube, df_scam_actions$risk_onlineTasks),2)
```

###### Post-hoc test

**Paper result**: The frequency of doing online tasks for money varies significantly between adults and teens. The following code tests whether the frequency of online tasks is still significantly associated with reporting the scam YouTube video when controlling for whether the participant is a teen or adult. From this, we see that frequency of online tasks is not a significant predictor when looking at adults  ($p_{uncorrected} = 0.876$) or teens alone ($p_{uncorrected} = 0.726$) This result is discussed in section 5D of the paper. 

```{r}
df_scam_actions_adult <- df_scam_actions %>% filter(adult == TRUE)
df_scam_actions_teen <- df_scam_actions %>% filter(adult == FALSE)
print("Comparison of reporting scam YouTube video vs frequency of doing online tasks for adults only")
CochranArmitageTest(table(df_scam_actions_adult$Report.the.video.to.YouTube, df_scam_actions_adult$risk_onlineTasks))
print("Comparison of reporting scam YouTube video vs frequency of doing online tasks for teens only")
CochranArmitageTest(table(df_scam_actions_teen$Report.the.video.to.YouTube, df_scam_actions_teen$risk_onlineTasks))
```

##### Visit the website
The following code tests which potential independent variables are significantly associated with recommending to visit the website shown in the scam YouTube video.
```{r}
scam_visit_results <- stat_test(dep_var = "Visit.the.website.s..shown.in.the.video", df=df_scam_actions)
```
**Paper result**: The following code prints results for variables that are significantly associated with recommending to visit the website shown in the scam YouTube video. The fact that visiting the website shown in scam YouTube video is significantly associated with stimuli shown is shown in figure 2a
```{r}
scam_visit_results %>% filter(significant == TRUE)
```  
The following code shows the rate of recommending to visit the website shown in the scam YouTube video by scam stimuli shown The rows represent whether the participant recommended visitng the scam website or not.   
```{r}
prop.table(table(df_scam_actions$Visit.the.website.s..shown.in.the.video, df_scam_actions$scam_condition), 2)
```

##### Leave a comments
The following code tests which potential independent variables are significantly associated with recommending to leave a comment on the scam YouTube video.
```{r}
scam_leavecomments_results <- stat_test(dep_var = "Leave.a.comment.on.the.video..please.specify.", df=df_scam_actions)
```
The following code shows that none of the potential explanatory variables are significantly associated with recommending to leave a commnet on the scam YouTube video. 
```{r}
scam_leavecomments_results %>% filter(significant == TRUE)
``` 
##### Look at comments
The following code tests which potential independent variables are significantly associated with recommending to look at the comments on the scam YouTube video.
```{r}
scam_lookcomments_results <- stat_test(dep_var = "Look.at.the.comments.on.the.video", df=df_scam_actions)
```
The following code shows that none of the potential explanatory variables are significantly associated with recommending to look at the commnets on the scam YouTube video. 
```{r}
scam_lookcomments_results %>% filter(significant == TRUE)
``` 

##### other
The following code tests which potential independent variables are significantly associated with recommending another action in response to the scam YouTube video.
```{r}
scam_other_results <- stat_test(dep_var = "Other..please.specify.", df=df_scam_actions)
```
The following code shows that none of the potential explanatory variables are significantly associated with recommending another action in response to the scam YouTube video. 
```{r}
scam_other_results %>% filter(significant == TRUE)
``` 

#### Scam website video comparisons
The following code splits the list of actions that the user recommended in response to the legit youtube videos into columns of booleans, with each boolean indicating whether or not an action was selected.For example, ```Exit.from.the.website.without.doing.anything``` is ```TRUE``` if the participant recommended that their friend exit the website. 
```{r}
splitup <- sapply(unlist(df_merged$scm_web), strsplit, ',')
headnames <- unique(unlist(splitup))
mat <- t(unname(sapply(splitup, function(x) headnames %in% x)))
colnames(mat) <- headnames
df_scm_web_actions <- data.frame(df_merged, mat)
```
##### Exit
The following code tests which potential independent variables are significantly associated with recommending exiting the scam website.
```{r}
scm_web_exit_results <- stat_test(dep_var = "Exit.from.the.website.without.doing.anything", df=df_scm_web_actions)
```
**Paper result**: The following code prints results for variables that are significantly associated with recommending to exit the scam website. The fact that recommending to exit the website varied by stimuli shown is shown in figure 2b and discussed in section 5B of the paper.
```{r}
scm_web_exit_results %>% filter(significant == TRUE)
```
The following code prints the rate of recommending to exit the scam website by scam stimuli shown. The rows represent whether or not the user recommended exiting from the scam website.
```{r}
prop.table(table(df_scm_web_actions$Exit.from.the.website.without.doing.anything, df_scm_web_actions$scam_condition),2)
```

##### Search online
The following code tests which potential independent variables are significantly associated with recommending searching online to learn more about the scam website.
```{r}
scm_web_search_results <- stat_test(dep_var = "Search.online.to.learn.more.about.the.website", df=df_scm_web_actions)
```
**Paper result**: The following code prints results for variables that are significantly associated with recommending to search online to learn more about the scam website. The fact that recommending to search online to learn more about the website varied by stimuli shown is shown in figure 2b and discussed in section 5B of the paper.
```{r}
scm_web_search_results %>% filter(significant == TRUE)
```
The following code prints the rate of recommending to search online to learn more about the scam website by scam stimuli shown. The rows represent whether or not the user recommended searching to learn more about the scam website.
```{r}
prop.table(table(df_scm_web_actions$Search.online.to.learn.more.about.the.website, df_scm_web_actions$scam_condition),2)
```

##### Follow all instructions
The following code tests which potential independent variables are significantly associated with recommending to follow the instructions from the scam video on the website.
```{r}
scm_follow_results <- stat_test(dep_var = "Follow.all.of.the.instructions.in.the.video.to.complete.the.offer", df=df_scm_web_actions)
```
The following code show that none of the tested independent variables are significantly associated with recommending to follow the instructions from the scam video on the website.
```{r}
scm_follow_results %>% filter(significant == TRUE)
```

##### Register for website
The following code tests which potential independent variables are significantly associated with recommending to register for the scam website. 
```{r}
scm_register_results <- stat_test(dep_var = "Register.for.the.website", df=df_scm_web_actions)
```
The following code shows that none of the tested independent variables are significantly associated with recommending to register for the scam website.
```{r}
scm_register_results %>% filter(significant == TRUE)
```

##### Ask for help
The following code combines the option presented to adults ("Ask a knowledgeable friend for help") with the option presented ot teens ("Ask a parent for help")
```{r}
df_scm_web_actions$Ask.for.help <- df_scm_web_actions$Ask.a.knowledgeable.friend.for.help | df_scm_web_actions$Ask.a.parent.for.help
```

The following code tests which potential independent variables are significantly associated with recommending to ask for help when viewing the scam website.
```{r}
scm_ask_for_help_results <- stat_test(dep_var = "Ask.for.help", df=df_scm_web_actions)
```
The following code shows that none of the tested independent variables are significantly associated with recommending to ask for help when viewing the scam website.
```{r}
scm_ask_for_help_results %>% filter(significant == TRUE)
```

##### Other
The following code tests which potential independent variables are significantly associated with recommending another action in response to the scam website. 
```{r}
scm_other_results <- stat_test(dep_var = "Other..please.specify.", df=df_scm_web_actions)
```
The following code shows that none of the tested independent variables are significantly associated with recommending another action in response to the scam website. 
```{r}
scm_other_results %>% filter(significant == TRUE)
```

### Thumbnail comparisons
The following code subsets the data to just the participants who saw Roblox stimuli and just participants who saw Spotify stimuli respectively.
```{r}
df_tn_roblox <- filter(df_merged, !is.na(roblox_tn_selection))
df_tn_spotify <- filter(df_merged, !is.na(spotify_tn_selection))
```

The following code prints a table showing the proportion of participants who mentioned looking at each feature in the search results. 
```{r}
table(unlist(str_split(df_merged$tn_parts, ",")))/nrow(df_merged)
```

The next two subsections run statistical testing for the Spotify and Roblox search result selection task indepdently. 
#### Spotify thumbnail comparisons
The following code first creates ```df_tn_spotify_wide``` by spliting the responses to the search result selection task into booleans where each boolean corresponds to whether the participant selected a particular search result was selected. The numbering is described in the dictionary file. For example, if the column```X3``` is ```TRUE``` then the participant selected the third clickbait search result. ```X10``` corresponds to the none of the thumbnails option. The code next creates ```df_tn_spotify_long```, This long version contains nine rows for each participant (one row for each search result), with the variable ```thumbnail``` indicating which search result the row represents and the variable ```selected``` indicating whether or not the participant selected the search result. For example, if the variable ```thumbnail``` is ```X9``` and the variable ```selected``` is ```FALSE```, then the participant indicated by the ```pid``` did not select the third scam video search result.
```{r}
splitup <- sapply(unlist(df_tn_spotify$spotify_tn_selection), strsplit, ',')
headnames <- c("1","2","3","4","5","6","7","8","9","10")
df_tn_spotify_wide <- data.frame(df_tn_spotify,(mat <- t(unname(sapply(splitup, function(x) headnames %in% x)))))
df_tn_spotify_long <- gather(df_tn_spotify_wide, thumbnail, selected, X1:X9, factor_key=TRUE)
```

**Paper Result**: The following code performs Cochran's Q test to determine whether the search results were selected at significantly different rates. It then performs pairwise Wilcoxon sign tests to compare search results to one another. The fact that the Spotify search results were selected at significantly different rates are discussed in section 5B of the paper. The fact that the legitimate search results were more often selected than the scam search results is also discussed in section 5B.
```{r}
xtabs(~selected + thumbnail, df_tn_spotify_long)
tn_spotify.qtest <- cochran.qtest(selected ~ thumbnail|pid, df_tn_spotify_long, p.method = "BH")
print(tn_spotify.qtest)
```

The following code computes the effect size measure $\eta^2_Q$
```{r}
# formula Q/(number of participants * (number of conditions - 1))
tn_spotify.qtest$statistic/(nrow(df_tn_spotify_wide)*(9-1))
```
The following subsections determine whether the rate of selecting particular search results are significantly associated with any of the tested independent variables.
##### Clickbait Search Result 1
The following code tests whether selecting the first clickbait search result is significantly associated with any of the tested independent variables.
```{r}
tn1_spotify_results <- stat_test("X1", df=df_tn_spotify_wide, test_condition = FALSE, stimuli_tyoe = "spotify")
```
The following code shows that none of the tested independent variables are significantly associated with selecting the first clickbait search result.
```{r}
tn1_roblox_results %>% filter(significant == TRUE)
```

##### Clickbait Search Result 2
The following code tests whether selecting the second clickbait search result is significantly associated with any of the tested independent variables.
```{r}
tn2_spotify_results <- stat_test("X2", df=df_tn_spotify_wide, test_condition = FALSE, stimuli_tyoe = "spotify")
```
The following code prints which independent variables are significantly associated with selecting the second clickbait search result.
```{r}
tn2_spotify_results %>% filter(significant == TRUE)
```
The following code prints the rate of selecting the second clickbait search result by time spent watching online videos per week.  The rows represent whether or not the participant selected the second clickbait search result.
```{r}
prop.table(table(df_tn_spotify_wide$X2, df_tn_spotify_wide$time_videos),2)
```

##### Clickbait Search Result 3
The following code tests whether selecting the third clickbait search result is significantly associated with any of the tested independent variables.
```{r}
tn3_spotify_results <- stat_test("X3", df=df_tn_spotify_wide, test_condition = FALSE, stimuli_tyoe = "spotify")
```
The following code shows that none of the tested independent variables are significantly associated with selecting the third clickbait search result.
```{r}
tn3_spotify_results %>% filter(significant == TRUE)
```

##### Legit Search Result 1
The following code tests whether selecting the first legitimate search result is significantly associated with any of the tested independent variables.
```{r}
tn4_spotify_results <- stat_test("X4", df=df_tn_spotify_wide, test_condition = FALSE, stimuli_tyoe = "spotify")
```
The following code shows that none of the tested independent variables are significantly associated with selecting the first legit search result.
```{r}
tn4_spotify_results %>% filter(significant == TRUE)
```
##### Legit Search Result 2
The following code tests whether selecting the second legitimate search result is significantly associated with any of the tested independent variables.
```{r}
tn5_spotify_results <- stat_test("X5", df=df_tn_spotify_wide, test_condition = FALSE, stimuli_tyoe = "spotify")
```
The following code shows that none of the tested independent variables are significantly associated with selecting the second legit search result.
```{r}
tn5_spotify_results %>% filter(significant == TRUE)
```
##### Legit Search Result 3
The following code tests whether selecting the third legitimate search result is significantly associated with any of the tested independent variables.
```{r}
tn6_spotify_results <- stat_test("X6", df=df_tn_spotify_wide, test_condition = FALSE, stimuli_tyoe = "spotify")
```
The following code shows that none of the tested independent variables are significantly associated with selecting the third legit search result.
```{r}
tn6_spotify_results %>% filter(significant == TRUE)
```
##### Scam Search Result 1
The following code tests whether selecting the first scam  search result is significantly associated with any of the tested independent variables.
```{r}
tn7_spotify_results <- stat_test("X7", df=df_tn_spotify_wide, test_condition = FALSE, stimuli_tyoe = "spotify")
```
The following code shows that none of the tested independent variables are significantly associated with selecting the first scam search result.
```{r}
tn7_spotify_results %>% filter(significant == TRUE)
```
##### Scam Search Result 2
The following code tests whether selecting the second scam  search result is significantly associated with any of the tested independent variables.
```{r}
tn8_spotify_results <- stat_test("X8", df=df_tn_spotify_wide, test_condition = FALSE, stimuli_tyoe = "spotify")
```
The following code prints which independent variables are significantly associated with selecting the second scam search result.
```{r}
tn8_spotify_results %>% filter(significant == TRUE)
```
The following code prints cross tables for significant results.  The rows represent whether or not the participant selected the second clickbait search result.
```{r}
print("Rate of selectin gthe second scam search result vs. frequency of using Spotify")
prop.table(table(df_tn_spotify_wide$X8, df_tn_spotify_wide$risk_usedSpotify),2)
```

```{r}
print("Rate of selecting the second scam search result vs. experience purchasing spotify premium")
prop.table(table(df_tn_spotify_wide$X8, df_tn_spotify_wide$risk_spotifyPremium),2)
```

```{r}
print("Rate of selecting the second scam search result vs. experience receiving free spotify premium")
prop.table(table(df_tn_spotify_wide$X8, df_tn_spotify_wide$risk_freeSpotify),2)
```

##### Scam Search Result 3
The following code tests whether selecting the third scam  search result is significantly associated with any of the tested independent variables.
```{r}
tn9_spotify_results <- stat_test("X9", df=df_tn_spotify_wide, test_condition = FALSE, stimuli_tyoe = "spotify")
```
The following code shows that none of the tested independent variables are significantly associated with selecting the third scam search result.
```{r}
tn9_spotify_results %>% filter(significant == TRUE)
```
##### No Search Results
The following code tests whether selecting none of the search results is significantly associated with any of the tested independent variables.
```{r}
no_answer_spotify_Stats_Results <- stat_test("X10", df=df_tn_spotify_wide, test_condition = FALSE, stimuli_tyoe = "spotify")
```
The following code shows that none of the tested independent variables are significantly associated with selecting none of the search results.
```{r}
no_answer_spotify_Stats_Results %>% filter(significant == TRUE)
```

### Compare Rbolox thumbnail
The following code first creates ```df_tn_roblox_wide``` by splitting the responses to the search result selection task into booleans where each boolean corresponds to whether the participant selected a particular search result. For example, if the column```X3``` is ```TRUE``` then the participant selected the third clickbait search result. ```X10``` corresponds to the none of the thumbnails option. The code next creates ```df_tn_roblox_long```, This long version contains nine rows for each participant (one row for each search result), with the variable ```thumbnail``` indicating which search result the row represents and the variable ```selected``` indicating whether or not the participant selected the search result. For example, if the variable ```thumbnail``` is ```X9``` and the variable ```selected``` is ```FALSE```, then the participant indicated by the ```pid``` did not select the third scam video search result.
```{r}
splitup <- sapply(unlist(df_tn_roblox$roblox_tn_selection), strsplit, ',')
headnames <- c("1","2","3","4","5","6","7","8","9","10")
df_tn_roblox_wide <- data.frame(df_tn_roblox,(mat <- t(unname(sapply(splitup, function(x) headnames %in% x)))))
df_tn_roblox_long <- gather(df_tn_roblox_wide, thumbnail, selected, X1:X9, factor_key=TRUE)
```

**Paper Result**: The following code performs Cochran's Q test to determine whether the search results were selected at significantly different rates. It then performs pairwise Wilcoxon sign tests to compare search results to one another. The fact that the Roblox search results were selected at significantly different rates are discussed in section 5B of the paper. The fact that the legitimate search results were more often selected than the scam search results is also discussed in section 5B.
```{r}
xtabs(~selected + thumbnail, df_tn_roblox_long)
tn_roblox.qtest <- cochran.qtest(selected ~ thumbnail|pid, df_tn_roblox_long, p.method = "BH")
print(tn_roblox.qtest)
```

The following code computes the effect size measure $\eta^2_Q$
```{r}
# formula Q/(number of participants * (number of conditions - 1))
tn_roblox.qtest$statistic/(nrow(df_tn_roblox_wide)*(9-1))
```

The following subsections determine whether the rate of selecting particular search results are significantly associated with any of the tested independent variables.

#### CLickbait Search Result 1
The following code tests whether selecting the first clickbait search result is significantly associated with any of the tested independent variables.
```{r}
tn1_roblox_results <- stat_test("X1", df=df_tn_roblox_wide, test_condition = FALSE, stimuli_tyoe = "roblox")
```
The following code shows that none of the tested independent variables are significantly associated with selecting the first clickbait search results.
```{r}
tn1_roblox_results %>% filter(significant == TRUE)
```

#### CLickbait Search Result 2
The following code tests whether selecting the second clickbait search result is significantly associated with any of the tested independent variables.
```{r}
tn2_roblox_results <- stat_test("X2", df=df_tn_roblox_wide, test_condition = FALSE, stimuli_tyoe = "roblox")
```
The following code shows that none of the tested independent variables are significantly associated with selecting the second clickbait search results.
```{r}
tn2_roblox_results %>% filter(significant == TRUE)
```


#### CLickbait Search Result 3
The following code tests whether selecting the third clickbait search result is significantly associated with any of the tested independent variables.
```{r}
tn3_roblox_results <- stat_test("X3", df=df_tn_roblox_wide, test_condition = FALSE, stimuli_tyoe = "roblox")
```
The following code shows that none of the tested independent variables are significantly associated with selecting the third clickbait search results.
```{r}
tn3_roblox_results %>% filter(significant == TRUE)
```
#### Legit Search Result 1
The following code tests whether selecting the first legit search result is significantly associated with any of the tested independent variables.
```{r}
tn4_roblox_results <- stat_test("X4", df=df_tn_roblox_wide, test_condition = FALSE, stimuli_tyoe = "roblox")
```
The following code shows that none of the tested independent variables are significantly associated with selecting the first legit search results.
```{r}
tn4_roblox_results %>% filter(significant == TRUE)
```
#### Legit Search Result 2
The following code tests whether selecting the second legit search result is significantly associated with any of the tested independent variables.
```{r}
tn5_roblox_results <- stat_test("X5", df=df_tn_roblox_wide, test_condition = FALSE, stimuli_tyoe = "roblox")
```
The following code prints which independent variables are significantly associated with selecting the second legit search result.
```{r}
tn5_roblox_results %>% filter(significant == TRUE)
```
The following code prints cross tables for significant results.  The rows represent whether or not the participant selected the second legit search result.
```{r}
print("Rate of selecting the second legit search result vs. frequency of playing Roblox")
prop.table(table(df_tn_roblox_wide$X5, df_tn_roblox_wide$risk_playedRoblox), 2)
```

```{r}
print("Rate of selecting the second legit search result vs. frequency of doing online tasks")
prop.table(table(df_tn_roblox_wide$X5, df_tn_roblox_wide$risk_onlineTasks), 2)
```

#### Legit Search Result 3
The following code tests whether selecting the third legit search result is significantly associated with any of the tested independent variables.
```{r}
tn6_roblox_results <- stat_test("X6", df=df_tn_roblox_wide, test_condition = FALSE, stimuli_tyoe = "roblox")
```
The following code shows that none of the tested independent variables are significantly associated with selecting the third legit search results.
```{r}
tn6_roblox_results %>% filter(significant == TRUE)
```

#### Scam Search Result 1
The following code tests whether selecting the first scam search result is significantly associated with any of the tested independent variables.
```{r}
tn7_roblox_results <- stat_test("X7", df=df_tn_roblox_wide, test_condition = FALSE, stimuli_tyoe = "roblox")
```
The following code shows that none of the tested independent variables are significantly associated with selecting the first scam search results.
```{r}
tn7_roblox_results %>% filter(significant == TRUE)
```

#### Scam Search Result 2
The following code tests whether selecting the second scam search result is significantly associated with any of the tested independent variables.
```{r}
tn8_roblox_results <- stat_test("X8", df=df_tn_roblox_wide, test_condition = FALSE, stimuli_tyoe = "roblox")
```

The following code prints which independent variables are significantly associated with selecting the second scam search result.
```{r}
tn8_roblox_results %>% filter(significant == TRUE)
```
The following code prints the rate of selecting the second scam search result by the frequency of playing Roblox. The rows represent whether or not hte partiicpant selected the second scam search result. 
```{r}
prop.table(table(df_tn_roblox_wide$X8, df_tn_roblox_wide$risk_playedRoblox), 2)
```
#### Scam Search Result 3
The following code tests whether selecting the third scam search result is significantly associated with any of the tested independent variables.
```{r}
tn9_roblox_results <- stat_test("X9", df=df_tn_roblox_wide, test_condition = FALSE, stimuli_tyoe = "roblox")
```

The following code shows that none of the tested independent variables are significantly associated with selecting the third scam search results.
```{r}
tn9_roblox_results %>% filter(significant == TRUE)
```


#### No Search Result selected
The following code tests whether selecting the no search results is significantly associated with any of the tested independent variables.
```{r}
no_thumbnails_result <- stat_test("X10", df=df_tn_roblox_wide, test_condition = FALSE, stimuli_tyoe = "roblox")
```

The following code prints which independent variables are significantly associated with selecting no search results.
```{r}
no_thumbnails_result %>% filter(significant == TRUE)
```

The following code prints the rate of selecting no search results by the frequency of playing Roblox. The rows represent whether or not the participant selected no search results. 
```{r}
prop.table(table(df_tn_roblox_wide$X10, df_tn_roblox_wide$risk_playedRoblox),2)
```




